\sysfull

### 2018-08-05 paper/asplos19/intro.tex
intro

Upon power failures, a device loses the volatile
state in its registers, stack, SRAM, and retains the state of any non-volatile
memory, such as FRAM. While capturing periodic
checkpoints~\cite{mementos,quickrecall} and sleep
scheduling~\cite{dewdrop,hibernus,hibernusplusplus} help preserve execution
progress, failures can leave non-volatile state incorrect, partially updated,
and may leave checkpointed volatile state inconsistent with non-volatile state.
These inconsistencies cause intermittent execution to deviate from
continuously-powered behavior, often leading to an unrecoverable
application failure~\cite{dino,edb}. Prior work developed two main approaches to deal with data inconsistency for
intermittently-powered devices: (i) \emph{software-based programming and
execution models}~\cite{dino,ratchet,chain,alpaca} and (ii)
\emph{hardware-based computer architecture
support}~\cite{hicks_isca_2017,idetic,nvp}. Complex architectural changes are
expensive to design, verify, and manufacture. New architectures are also
inapplicable to existing systems~\cite{hicks_isca_2017,nvp}. Software
approaches are simpler and applicable to existing devices today. Therefore, this work focuses on a key limitation of task-based software approaches, that is, the {\em inflexibility} of statically decomposing a program into tasks.

%
\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/intro-figure-vert.pdf}
    \caption{\note{small static task subplot and large static task subplot can be re-arranged to fit next to each other, so we end up with two layers plot} Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{C}) of individual tasks (denoted as \texttt{Tx}). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}
%
%\textbf{Task Decomposition of Intermittent Programs.}

\noindent\textbf{Crucial Drawback of Static Task Decomposition.} 
\note{Why no indent?}
Task-based programming and execution models require a
programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to
statically decompose a program into a collection of tasks. A \emph{task}, a top level function, can
include arbitrary computation that should be executed despite arbitrarily-timed power failures.
The programmer (or a compiler) explicitly expresses task-to-task control flow.
Fig.~\ref{fig:coalesce} illustrates how a program's tasks execute and shows how tasks transitions can impose a runtime overhead. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at runtime.
%
A programmer may thus create very large tasks in an attempt to reduce task transitions
overhead. However, a very large task may require more energy to complete than a device's fixed hardware energy
buffer can hold which may lead to a task \emph{non-termination} problem. To eliminate this risk,
existing systems require the programmer to decompose a program into relatively small tasks to preserve execution progress. These constraints on task sizing lead to the following dilemma: should large tasks be used, that are efficient but risk non-termination, or small tasks that are guaranteed to complete, but incur a high task transition and commit overhead. In this work,
we propose a third way, using a novel technique called \emph{adaptive task size execution by task coalescing/splitting} that efficiently executes small tasks, trimming unnecessary overheads, while avoiding the risk of non-termination.

\noindent\textbf{Challenges and Contributions.}
\note{Why no indent?}
This paper introduces a new system called \emph{\sys}, which executes a task-based
intermittent program by \emph{dynamically} coalescing/splitting its tasks.
\sys accepts any static decomposition and it coalesces (groups) tasks (Fig.~\ref{fig:coalesce}, top) or splits them (Fig.~\ref{fig:coalesce},bottom) based on the estimated energy availability without demanding any hardware support. The unique challenges and contributions revealed by this work are listed below:
\note{it takes more space, but a bullet list makes C1-C3 stand out more properly}

>>>>

Upon power failures, a device loses the volatile
state in its registers, stack, SRAM, and retains the state of any non-volatile
memory, such as FRAM. While capturing periodic
checkpoints~\cite{mementos,quickrecall} and sleep
scheduling~\cite{dewdrop,hibernus,hibernusplusplus} help preserve execution
progress, failures can leave non-volatile state incorrect, partially updated,
and may leave checkpointed volatile state inconsistent with non-volatile state.
These inconsistencies cause intermittent execution to deviate from
continuously-powered behavior, often leading to an unrecoverable
application failure~\cite{dino,edb}. Prior work developed two main approaches to deal with data inconsistency for
intermittently-powered devices: (i) \emph{software-based programming and
execution models}~\cite{dino,ratchet,chain,alpaca} and (ii)
\emph{hardware-based computer architecture
support}~\cite{hicks_isca_2017,idetic,nvp}. Complex architectural changes are
expensive to design, verify, and manufacture. New architectures are also
inapplicable to existing systems~\cite{hicks_isca_2017,nvp}. Software
approaches are simpler and applicable to existing devices today. \note{Talk about CP-based systems and talk why we focused task-based instead...}Therefore, this work focuses on a key limitation of task-based software approaches, that is, the {\em inflexibility} of statically decomposing a program into tasks.

%
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/intro-figure-v3.pdf}
    \caption{\note{small static task subplot and large static task subplot can be re-arranged to fit next to each other, so we end up with two layers plot} Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{C}) of individual tasks (denoted as \texttt{Tx}). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}
%
%\textbf{Task Decomposition of Intermittent Programs.}

\noindent\textbf{Crucial Drawback of Static Task Decomposition.} 
\note{Why no indent?}
Task-based programming and execution models require a
programmer~\cite{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to
statically decompose a program into a collection of tasks. A \emph{task}, a top level function, can
include arbitrary computation that should be executed despite arbitrarily-timed power failures.
The programmer (or a compiler) explicitly expresses task-to-task control flow.
Fig.~\ref{fig:coalesce} illustrates how a program's tasks execute and shows how tasks transitions can impose a runtime overhead. At each transition, the system incurs an overhead to track and atomically commit modifications to the non-volatile memory, to maintain consistency of program state~\cite{chain,alpaca}. The more task transitions a program requires, the more commit overhead is incurred by the system at runtime.
%
A programmer may thus create very large tasks in an attempt to reduce task transitions
overhead. However, a very large task may require more energy to complete than a device's fixed hardware energy
buffer can hold which may lead to a task \emph{non-termination} problem. To eliminate this risk,
existing systems require the programmer to decompose a program into relatively small tasks to preserve execution progress. These constraints on task sizing lead to the following dilemma: should large tasks be used, that are efficient but risk non-termination, or small tasks that are guaranteed to complete, but incur a high task transition and commit overhead.

\noindent\textbf{Challenges and Contributions.}
\note{Why no indent?}
This paper introduces \sys, a new task-based system that employs \emph{adaptive task size execution by task coalescing/splitting}. By means of this novel technique, small tasks can be executed efficiently by trimming unnecessary overheads \emph{dynamically}, meanwhile avoiding the risk of non-termination. \sys accepts any static decomposition and it coalesces (groups) tasks (Fig.~\ref{fig:coalesce}, top) or splits them (Fig.~\ref{fig:coalesce},bottom) based on the estimated energy availability without demanding any hardware support. \note{\textbf{To the best of our knowledge, \sys is the only task-based system that guarantees task termination and ....(something related with Coalescing...)  }}

The unique challenges and contributions revealed by this work are listed below:
\note{it takes more space, but a bullet list makes C1-C3 stand out more properly}
